### 2018-08-22 TeX/organigram1.tex
changed names

		%% organisms
		% id nodes
		\node (taxon) [ids, below of=cas, yshift=-9cm, align = center] {Taxon}; % \\ {(Genus or Species)}}; % escape brackets usin curly brackets
		% main nodes
		\node (taxonquery) [main, right of=taxon, xshift = 4.5cm, yshift = 3cm] {Taxonomy};
		\node (habitat) [main, right of=taxon, xshift = 4.5cm, yshift = 1cm] {Habitats}
			child { node { WORMS data base - \textbf{tx\_worms.R} }}
			child { node { Manual Search - \textbf{ha\_manual.R} }};
		\node (region) [main, right of = taxon, xshift = 4.5cm, yshift = -2cm] {Continents}
			child { node { GBIF - \textbf{qu\_gbif.R} }};

		%% final result
		\begin{pgfonlayer}{bg3}
			\node[rectangle, draw, rounded corners, minimum height = 2cm, minimum width = 7cm, fill = gray!10] (appbox) at (20.5cm,-10cm) {};
		\end{pgfonlayer}
		\node (apptext) [above of = appbox, yshift = 0.25cm, xshift = -3cm] {Etox-Base App}; 
		\node (testres) [res, right of = cas, xshift = 14cm, yshift = -5cm] {Result};
		\node (filtres) [res, right of = testres, xshift = 2cm] {Filter};
		\node (aggres) [res, right of = filtres, xshift = 2cm] {Aggregate};

>>>>

		%% organisms
		% id nodes
		\node (taxon) [ids, below of=cas, yshift=-9cm, align = center] {Taxon}; % \\ {(Genus or Species)}}; % escape brackets usin curly brackets
		% main nodes
		\node (taxonquery) [main, right of=taxon, xshift = 4.5cm, yshift = 3cm] {Taxonomy};
		\node (habitat) [main, right of=taxon, xshift = 4.5cm, yshift = 1cm] {Habitats}
			child { node { WORMS data base - \textbf{tx\_worms.R} }}
			child { node { Manual Search - \textbf{ha\_manual.R} }};
		\node (region) [main, right of = taxon, xshift = 4.5cm, yshift = -2cm] {Regions}
			child { node { GBIF - \textbf{qu\_gbif.R} }};

		%% final result
		\begin{pgfonlayer}{bg3}
			\node[rectangle, draw, rounded corners, minimum height = 2cm, minimum width = 7cm, fill = gray!10] (appbox) at (20.5cm,-10cm) {};
		\end{pgfonlayer}
		\node (apptext) [above of = appbox, yshift = 0.25cm, xshift = -3cm] {Etox-Base Function}; 
		\node (testres) [res, right of = cas, xshift = 14cm, yshift = -5cm] {Result};
		\node (filtres) [res, right of = testres, xshift = 2cm] {Filter};
		\node (aggres) [res, right of = filtres, xshift = 2cm] {Aggregate};
